### 2015-02-27 icfp15-servo/browsers.tex
Clarify parsing description.

  <script>
  document.write(``<!-'');
  </script>-
  This is commented
</html>
\end{lstlisting}
This requirement causes parsing to pause while JavaScript code is running.
But, since resource loading is such a large factor in the latency of loading many webpages (particularly on mobile),
all modern parsers also perform token stream scanning and prefetch of resources likely to be required~\cite{browsers-slow-smartphones}.

>>>>

  <script>
  document.write(``<!-'');
  </script>-
  This is commented
</html>
\end{lstlisting}
This requires parsing to pause until JavaScript code has run to completion.
But, since resource loading is such a large factor in the latency of loading many webpages (particularly on mobile),
all modern parsers also perform speculative token stream scanning and prefetch of resources likely to be required~\cite{browsers-slow-smartphones}.
